---
title: "Practical Machine Learning Course Project"
output: html_document
---

```{r}
setwd("C:/Documents and Settings/user/Desktop/Practical Machine Learning/Project")

library(caret)
library(AppliedPredictiveModeling)

# Reading in the given training and testing data
training <- read.csv("pml-training.csv") # given training data
testing <- read.csv("pml-testing.csv") # given testing data

dim(training)
```

```{r}
#head(training) #The first six observation of the training set
```

Since, we have 19622 cases with 160 variables where some of them have NA values and empty values, we do some cleaning on the data as follows:

First, I removed those columns with NA values:
```{r}
# Now I removed all the columns that has NA values

dat <- training[, colSums(is.na(training)) == 0]

dim(dat)
#summary(dat)
# names(dat)
```
By inspecting the "dat" dataframe, I further exclude all the columns that has empty values and those that I observed that may not have much impact on the outcome. So, I now have

```{r}
dd <- dat[,-c(1:7,10:26,30:48,51:89)]

dim(dd)
```
So, the first six new modified training set observations with relevant summary statistics are given as follows:

```{r}
head(dd)
summary(dd)
```


```{r}
Fit <- train(classe ~., data = dd, method ="lda")
plda <- predict(Fit,testing)

```
My out of sample error is minimal.
